BareTag Tool-Tracker

### 2024-10-15 draft.tex
wrote abstract

\title{ BareTag Tool-Tracker}
\author{ Walter Tebbetts, Sean Brown, Ken Su, and Connor McGarry }
\date{\today}

@@

% Optional TOC
% \tableofcontents
% \pagebreak

%--Paper--

@@

\pagebreak
\section{Section 2}
Lorem Ipsum \\

>>>>

\title{ BareTag Tool-Tracker}
\author{ Walter Tebbetts, CompE, Sean Brown, CompE, \\ Ken Su, CompE, and Connor McGarry, CompE}
\date{October 14, 2024}

@@

\begin{abstract}
    Over the past 10 years, the majority of tools on a construction 
    site have converted from wired to battery-powered. While this 
    makes tools easy to move around, it also makes them easy to misplace
    and an easier target for theives. Data indicates that the construction
    idustry suffered nearly \$1,000,000,000 in loses due to tool theft in
    2023 alone [1], strongly indicating the need for a robust and effective 
    theft mitigation system. We propose the BareTag Tool-Tracker, a novel
    approach to tool tracking that utilizes Ultra-Wideband(UWB) and Bluetooth 
    Low-Energy(BLE) radio in order to real-time track tools, materials, or other 
    valuable items on a construction site. The system utilizes a series
    of pre-placed Anchor posts, that send UWB pings to a Tag that is connected
    to a tool. Each Anchor can then calculate its distance to a Tag, relaying
    that information to a Base station over Long Range(LoRa) radio. The 
    base station runs the aggregated distance data through a multilateration
    algorithm that can calculate the Tag's location with $\pm$ 10 cm accuracy.
    The calculated location is then output to a local terminal, as well as 
    uploaded to a cloud database for future reference. Altogether, the BareTag Tool-Tracker
    is highly accurate ($\pm$ 10 cm), low-power (1 year of battery life), and
    scalable (increase range by adding additional Anchors).

\end{abstract}

@@

\pagebreak
\section{Section 2}
Lorem Ipsum \\ h
